---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# researchfunctions

<!-- badges: start -->
<!-- badges: end -->

The goal of researchfunctions is to allow me to keep all my functions for my project in one place.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("dakthomps00/researchfunctions")
```
## Example

This is a basic example which shows you how to solve a common problem:

Say we want to get confidence intervals of effect sizes for random normally distributed data sets we would do this

```{r example}
library(researchfunctions)

cohen <- replicate(10000, cohensd_OG(75,0,1,1))
mad <- replicate(10000, deltamad_OG(75,0,1,1))

confidint(cohen, 75)
confidint(mad,75)
```
This is another basic example which shows you how to solve a common problem:

Say we want to get confidence intervals of effect sizes for random normally distributed data sets that are contaminated with another normally distributed data set, we would do this

```{r}
library(researchfunctions)

cohen <- replicate(10000, cohensd_A(75,0.8,0.2,0,1,1.5,1,1,0.5))
mad <- replicate(10000, deltamad_A(75,0.8,0.2,0,1,1.5,1,1,0.5))

cohen1 <- t(cohen)
mad1 <- t(mad)

confidint(cohen1[,1], 75)
confidint(mad1[,1],75)
```
This is another basic example which shows you how to solve a common problem:

Say we want to get confidence intervals of effect sizes for random normally distributed data sets that are contaminated with a uniform data set, we would do this

```{r}
library(researchfunctions)

cohen <- replicate(10000, cohensd_B(75,0.8,0.2,0,1,1.5,1,1,2))
mad <- replicate(10000, deltamad_B(75,0.8,0.2,0,1,1.5,1,1,2))

cohen1 <- t(cohen)
mad1 <- t(mad)

confidint(cohen1[,1], 75)
confidint(mad1[,1],75)
```

